---
title: "Reproduction of Song et al. (2018) plots using the cmcR package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Song et al. (2018) reproduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup,echo=TRUE,message=FALSE,warning=FALSE}
library(cmcR)
library(magrittr)
library(ggplot2)
library(purrr)
library(dplyr)
library(x3ptools)
library(rgl)
set.seed(4132020)
```
  
<!-- TODO: -->
<!--   - Add hyperlinks to .png images of original plots -->
<!--   - Add red squares indicating non-CMCs based on topResultsPerCell output -->
<!--   - For RGL images - high contrast lighting. Use x3p_lighter(). Look into rgl for different lighting choices too. -->
<!--   - Try linear scale first -->
<!--   - create custom scale function where breaks happen at quintiles (median == white, max and min are dark orange and dark blue, respectively.) -->
<!--   - CCF map plot - show custom labels -- show 0, min, and max -->

<!--   This vignette will give `R` code to reproduce (at least qualitatively if not precisely) plots in Tong et al. (2018) using the `cmcR` package. -->
  
## Set-up
  
For the sake of an example we will consider 3 cartridge cases are from Fadul et al. (2011). The data are openly available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/). Specifically, we will consider the comparisons between "Fadul 1-1" and "Fadul 1-2" (available [here](https://tsapps.nist.gov/NRBTD/Studies/Firearm/Details/681f3cdf-8b1c-418a-af71-f52fd235e3da)) and "Fadul 2-1" (available [here](https://tsapps.nist.gov/NRBTD/Studies/Firearm/Details/12e0f761-2528-4e7b-8600-360bbb788537)). Note that Fadul 1-1 and Fadul 1-2 are known to have been fired from the same firearm while Fadul 2-1 was fired from a different firearm.
  
  <!-- The pseudocode below shows how you can read an x3p file into `R` and perform the necessary pre-processing procedures on the surface matrix therein before applying the CMC method. Note that the package defaults (as of 4/13/20) are to perform the following: -->

  <!-- 1. Downsample the surface matrix by a factor of 4 (i.e., sample every other row/column from the surface matrix) -->

  <!-- 2. Identify the breech face impression height value in the surface matrix using the RANSAC (Random Sample Consensus method). -->

  <!-- 3. Take the residuals between the RANSAC-fitted plane and the observed values in the surface matrix within a small `highSelectionThresh` threshold. -->

  <!-- 4. Remove rows/columns on the exterior of the resulting breech face impression surface matrix. -->

  <!-- 5. Detect and remove any observations within the firing pin impression circle on the interior of the breech face impression surface matrix. -->

  <!-- 6. Apply a Gaussian bandpass filter to the resulting surface matrix with wavelength cutoffs 16 and 250 microns $(\mu m)$. -->

  <!-- This is all done within the `selectBFImpression_sample_x3p` function. See [the documentation](https://jzemmels.github.io/cmcR/reference/selectBFImpression_sample_x3p.html) for this function for more information. Note that the RANSAC method relies on randomly sampling points from the surface matrix. Thus results have been seen to vary, albeit slightly, between applications. Thus, a seed is set for reproducibility purposes. -->

## Cartridge case scan image (Figure 1.1)

The `rgl` package can be used to visualize the cartridge case scans in 3 dimensions. The code below shows how to construct an `rgl` "scene" including placing lights at desired locations and controlling color, surface reflectance, etc. Each `rgl` scene can support up to 8 lights, but two are setup in the scene below - one directly above the scan at $(0,0,10)$ and another located "north-by-northwest" of the scan at $(-1,2,2)$. Note that these positions are relative to where the viewer begins - which is somewhere along the $z$-axis depending on the value provided to the `zoom` attribute. Based on experimentation, it appears that applying a Gaussian filter to the surface matrix prior to setting up the scene makes the breech face impressions more visually distinct (otherwise, a good deal of noise due to the scanning process makes it difficult to see much structure). There's truly an arbitrary amount of tinkering one could perform to get the "best" looking scene for a particular cartridge case scan, so in no way is the scene setup shown below generalizable to more cartridge case scans. Ince the `rgl` device is opened, the `x3ptools::x3p_snapshot` function saves the device's current viewpoint as a .png in a local directly called bfScanImages. The same procedure is carried out for the `x3p2` object (not shown).

To learn more about how various aspects of a scene are constructed, see [this vignette](https://cran.r-project.org/web/packages/rgl/vignettes/rgl.html) for the `rgl` package. For more details on using `rgl` specifically applied to .x3p files, see the documentation for the [`x3ptools` package on Github](https://github.com/heike/x3ptools).


```{r include=FALSE,eval=FALSE}
x3ptools::read_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/2d9cc51f-6f66-40a0-973a-a9292dbee36d") %>%
  x3ptools::image_x3p(file = "bfScanImages/fadul1-1.png",col = "white",zoom = .7,size = c(300,300))

x3ptools::read_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/cb296c98-39f5-46eb-abff-320a2f5568e8") %>%
  x3ptools::image_x3p(file = "bfScanImages/fadul1-2.png",col = "white",zoom = .7,size = c(300,300))
```

```{r}
if(!dir.exists("bfScanImages")){
  dir.create("bfScanImages")
}

x3p1 <- x3ptools::read_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/2d9cc51f-6f66-40a0-973a-a9292dbee36d")
x3p2 <- x3ptools::read_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/cb296c98-39f5-46eb-abff-320a2f5568e8")


#apply lowpass filter to reduce noise in scan:
surface1 <- x3p1$surface.matrix %>%
  cmcR::preProcess_gaussFilter(res = 3.125e-06,wavelength = 16,filtertype = "lp")
surface2 <- x3p2$surface.matrix %>%
  cmcR::preProcess_gaussFilter(res = 3.125e-06,wavelength = 16,filtertype = "lp")

params <- rgl::r3dDefaults

zoom = .7
size = c(300,300)

params$windowRect <- c(40, 125, 40 + size[1], 125 + size[2])
params$userMatrix <- diag(c(1, 1, 1, 1))
params$zoom <- zoom

#opens blank "canvas" upon which we can add lights, surfaces, etc.
open3d(params = params)

#removes any previously declared lights in scene
rgl.pop("lights")

#set-up two lights for scene -- a lot of experimentation possible here
light3d(x = -1,y = 1,z = 2,viewpoint.rel = TRUE,ambient = "white",diffuse = "white",specular = "white")
light3d(x = 0,y = 0,z = 10,ambient = "grey60",diffuse = "grey50",specular = "grey60",viewpoint.rel = TRUE)

#setup surface visualization
multiply <- 1 #x3ptools::image_x3p default to exaggerate relief
z <- multiply * surface1 # Exaggerate the relief
yidx <- ncol(z):1
y <- x3p1$header.info$incrementY * yidx
x <- x3p1$header.info$incrementX * (1:nrow(z))

# emission, specular, ambient affect how the surface interacts with lights --
# again, a lot of possible experimentation
surface3d(x, y, z, back = "filled",emission = "grey30",specular = "grey50",ambient = "grey10")

x3ptools::x3p_snapshot(file = "bfScanImages/fadul1-1.png")

rgl.close()
```

```{r include=FALSE}
#opens blank "canvas" upon which we can add lights, surfaces, etc.
open3d(params = params)

#removes any previously declared lights in scene
rgl.pop("lights")

#set-up two lights for scene -- a lot of experimentation possible here
light3d(x = -1,y = 1,z = 2,viewpoint.rel = TRUE,ambient = "white",diffuse = "white",specular = "white")
light3d(x = 0,y = 0,z = 10,ambient = "grey60",diffuse = "grey50",specular = "grey60",viewpoint.rel = TRUE)

#setup surface visualization
multiply <- 1 #x3ptools::image_x3p default to exaggerate relief
z <- multiply * surface2 # Exaggerate the relief
yidx <- ncol(z):1
y <- x3p2$header.info$incrementY * yidx
x <- x3p2$header.info$incrementX * (1:nrow(z))

# emission, specular, ambient affect how the surface interacts with lights --
# again, a lot of possible experimentation
surface3d(x, y, z, back = "filled",emission = "grey30",specular = "grey50",ambient = "grey10")

x3ptools::x3p_snapshot(file = "bfScanImages/fadul1-2.png")

rgl.close()
```

TODO:

The `magick` package can be used to read these .png files back into `R` for visualization. We can see the x3p scan snapshots below.

```{r}
magick::image_append(c(magick::image_read("bfScanImages/fadul1-1.png"),
                       magick::image_read("bfScanImages/fadul1-2.png"))) %>%
  plot()
```

## Processed Cartrige Case Scan (Figure 5)

Plotting the cartridge case surface matrix in which height values are mapped to a divergent color scheme may help highlight breech face impressions. We can use `ggplot2` to accomplish this.

```{r}
fadul1.1 <- cmcR::selectBFImpression_sample_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/2d9cc51f-6f66-40a0-973a-a9292dbee36d")
fadul1.2 <- cmcR::selectBFImpression_sample_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/cb296c98-39f5-46eb-abff-320a2f5568e8")
fadul2.1 <- cmcR::selectBFImpression_sample_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/8ae0b86d-210a-41fd-ad75-8212f9522f96")
```

```{r include=FALSE,eval=FALSE}
#if we want to include more pairs in the comparison
fadul2.2 <- cmcR::selectBFImpression_sample_x3p("https://tsapps.nist.gov/NRBTD/Studies/CartridgeMeasurement/DownloadMeasurement/702956c6-4d7d-4cc5-be62-219b788dc7b0")
```


```{r}
cmcR::x3pListPlot(x3pList = list("Fadul 1-1" = fadul1.1$x3p,"Fadul 1-2" = fadul1.2$x3p),
                  type = "faceted",
                  rotate = 90)
```

## CMC Plot (Figure 4)

The code below will perform the cell-based comparison procedure and then determine the initial/high CMCs for the known match and known non-match pairs of cartridge cases. The "initial" CMCs are determined based on the originally proposed method from Song (2013) while the "high" CMCs are determined using the "High CMC" method proposed by Tong et al. (2015).

```{r}
# undebug(cmcR:::checkForBreechface)
# debug(cmcR:::cellCCF)

kmComparison <- cmcR::cellCCF_bothDirections(x3p1 = fadul1.1$x3p,
                                             x3p2 = fadul1.2$x3p,
                                             cellNumHoriz = 8,
                                             minObservedProp = .1,
                                             regionToCellProp = 9)

knmComparison <- cmcR::cellCCF_bothDirections(x3p1 = fadul1.1$x3p,
                                              x3p2 = fadul2.1$x3p,
                                              cellNumHoriz = 8,
                                              minObservedProp = .1,
                                              regionToCellProp = 9)

kmCMC <- cmcR::cmcFilter_improved(kmComparison,
                         ccf_thresh = .5,
                         dx_thresh = 20,
                         theta_thresh = 6)

knmCMC <- cmcR::cmcFilter_improved(knmComparison,
                         ccf_thresh = .5,
                         dx_thresh = 20,
                         theta_thresh = 6)
```

We can then visualize the CMCs for these comarisons. Below are the high CMCs for the known match pair.

```{r}
# debugonce(cmcR:::x3pListPlot)
kmPlts <- cmcR::cmcPlot(x3p1 = fadul1.1$x3p,
                        x3p2 = fadul1.2$x3p,
                        cellCCF_bothDirections_output = kmComparison,
                        cmcFilter_improved_output = kmCMC,
                        type = "faceted")
kmPlts$highCMC
```

The known non-match pair didn't yield any high CMCs, so we can only visualize the initial CMCs.

```{r}
# debug(cmcR:::arrangeCMCPlot)

knmPlts <- cmcR::cmcPlot(x3p1 = fadul1.1$x3p,
                   x3p2 = fadul2.1$x3p,
                   cellCCF_bothDirections_output = knmComparison,
                   cmcFilter_improved_output = knmCMC)

knmPlts$initialCMC
```

## Bonus: CCF "Map"

```{r}
kmCellRegionPairs <- cmcR::getCellRegionPairs(fadul1.1$x3p,fadul1.2$x3p,ccfDF = kmCMC$highCMCs,cellCCF_params = kmComparison$comparison_1to2$params)

kmCellRegionPairs[3] %>%
  map2(.x = .,
       .y = names(.), 
       function(set,theta){
         map(set[5], ~ ccfMapPlot(mat1 = .[[1]],
                          mat2 = .[[2]],
                          theta = theta,
                          type = "raster"))
         })
```


<!-- The cartridge cases after pre-processing can be visualized quickly by first converting the surface matrices into the `imager` package's datatype `cimg`. The base `plot` function interacts fairly well with `cimg` objects. -->

<!-- ```{r} -->
<!-- par(mar = c(1,1,1,1)) -->

<!-- imlist("Fadul 1-1" = as.cimg(fadul1.1$x3p$surface.matrix), -->
<!--        "Fadul 1-2" = as.cimg(fadul1.2$x3p$surface.matrix), -->
<!--        "Fadul 2-1" = as.cimg(fadul2.1$x3p$surface.matrix), -->
<!--        "Fadul 2-2" = as.cimg(fadul2.2$x3p$surface.matrix)) %>% -->
<!--   plot() -->
<!-- ``` -->

<!-- Now the cartridge cases are ready to be compared. This is done below using the `cellCCF_bothDirections` function for each KM and KNM pairing (so 6 in total). Note that we are considering the rangle of rotation values from -30 to 30 degrees and using a grid of 8 by 8 cells. The code here is written in a way to be at least somewhat generalizable (e.g., using the `purrr::map` family) if the reader is interested in applying the method to a larger set of cartridge cases. -->

<!-- ```{r} -->
<!-- kmPairs <- list("1.1_1.2" = list(fadul1.1$x3p,fadul1.2$x3p), -->
<!--                 "2.1_2.2" = list(fadul2.1$x3p,fadul2.2$x3p)) -->

<!-- knmPairs <- list("1.1_2.1" = list(fadul1.1$x3p,fadul2.1$x3p), -->
<!--                  "1.1_2.2" = list(fadul1.1$x3p,fadul2.2$x3p), -->
<!--                  "1.2_2.1" = list(fadul1.2$x3p,fadul2.1$x3p), -->
<!--                  "1.2_2.2" = list(fadul1.2$x3p,fadul2.2$x3p)) -->

<!-- kmComparisons <- kmPairs %>% -->
<!--   map(~ cmcR::cellCCF_bothDirections(.[[1]],.[[2]], -->
<!--                                      thetas = seq(-30,30,by = 3), -->
<!--                                      cellNumHoriz = 8)) -->

<!-- knmComparisons <- knmPairs %>% -->
<!--   map(~ cmcR::cellCCF_bothDirections(.[[1]],.[[2]], -->
<!--                                      thetas = seq(-30,30,by = 3), -->
<!--                                      cellNumHoriz = 8)) -->
<!-- ``` -->

<!-- With the comparisons completed, we can now show how to reproduce a variety of plots commonly given in the CMC literature. -->

<!-- ### CMC-$\theta$ distribution -->

<!-- Tong et al. (2015) discusses an improvement to the CMC method originally proposed by Song (2013). Figures 2 and 3 of Tong et al. (2015) show how the CMC count varies across a variety of rotation values for a known match pair and a known non-match pair of cartridges cases, respectively. For a truly matching pair of cartridge cases, this "CMC-$\theta$ distribution" tends to attain a mode around the rotation value that correctly aligns one to the other. This tendency can be used to determine, for example, if comparing one cartridge case scan to another in one "direction" yields a CMC-$\theta$ mode that agrees the comparison in the other direction up to a sign.  -->

<!-- The plot below illustrates this by showing the CMC-$\theta$ for the known match Fadul 1-1 and Fadul 1-2 pair. The `cmcPerThetaBarPlot` function is used to construct the plot. Comparing Fadul 1-1 to Fadul 1-2 (i.e., Fadul 1-1 is partitioned into a grid of cells and compared to larger regions in Fadul 1-2) clearly yields a CMC-$\theta$ mode around -24 degrees (i.e., Fadul 1-2 should be rotated -24 degrees to align with Fadul 1-1). In the other direction, we see that comparing Fadul 1-2 to Fadul 1-1 yields a CMC-$\theta$ mode around 21, which indicates that both directions agree (at least within a tolerance of, say, 3 degrees).  -->

<!-- The way that Tong et al. propose to identify modes in the CMC-$\theta$ distribution is to introduce a "high CMC" threshold equal to the max CMC count minus some constant. That is, $CMC_{\text{high}} = CMC_{\max} - \tau$ for some $\tau$. Using this high CMC threshold, we can determine how spread out the high CMC $\theta$ values are; the motivation here being that excessively diffuse high CMC $\theta$ values indicate that little "consensus" is reached as to the correct $\theta$ rotation value and the cartridge case pair under consideration is likely not a match. -->

<!-- ```{r} -->
<!-- cmcR::cmcPerThetaBarPlot(kmComparisons$`1.1_1.2`, -->
<!--                          ccf_thresh = .6, -->
<!--                          dx_thresh = 10, -->
<!--                          highCMCThresh = 1) -->
<!-- ``` -->

<!-- In contrast, we can see the CMC-$\theta$ distribution for the known non-match pair of Fadul 1-1 and Fadul 2-1. Following the high CMC criterion discussed above, we can see that the range of $\theta$ values that we would classify as having a high CMC count is rather spread out (-18 to 3 degrees in one direction vs. -12 to 21 degrees in the other). Thus, we would conclude that this cartridge case pair is likely not a match. -->

<!-- ```{r} -->
<!-- cmcR::cmcPerThetaBarPlot(knmComparisons$`1.1_2.1`, -->
<!--                          ccf_thresh = .6, -->
<!--                          dx_thresh = 10, -->
<!--                          highCMCThresh = 1) -->
<!-- ``` -->

<!-- ### CCF Map -->

<!-- We may be interested in learning more about a particular comparison that was done between a pair of cartridge case scans. For example, as discussed above it appears that Fadul 1-1 and Fadul 1-2 align well for a rotation of 24 degrees (-24 depending on the direction). We may be interested in what the cell/region pairs looked like just before the CCF was computed. The `getCellRegionPairs` function will take a data frame of CCF results, such as the one associated with the comparison after Fadul 1-2 is rotated -24 degrees, and return each cell/region pair represented in that data frame. For brevity, we'll just consider as examples the Fadul 1-1 and Fadul 1-2 comparison as well as the Fadul 1-1 and Fadul 2-1 comparison. -->

<!-- ```{r} -->
<!-- kmCellRegionPairs <- cmcR::getCellRegionPairs(x3p1 = fadul1.1$x3p, -->
<!--                                               x3p2 = fadul1.2$x3p, -->
<!--                                               ccfDF = kmComparisons$`1.1_1.2`$comparison_1to2$ccfResults$`-24`, -->
<!--                                               params = kmComparisons$`1.1_1.2`$comparison_1to2$params) -->

<!-- knmCellRegionPairs <- cmcR::getCellRegionPairs(x3p1 = fadul1.1$x3p, -->
<!--                                                x3p2 = fadul2.1$x3p, -->
<!--                                                ccfDF = knmComparisons$`1.1_2.1`$comparison_1to2$ccfResults$`-9`, -->
<!--                                                params = knmComparisons$`1.1_2.1`$comparison_1to2$params) -->
<!-- ``` -->


<!-- Figures 4 and 5 in Tong et al. (2015) show examples of "CCF maps," as they are aptly called, for a known match cell/region pair and a known non-match cell/region pair, respectively. These "maps" are actually just the 3-dimensional cross-correlation function surface. They are referred as maps because they indicate what the CCF is for various translation values of one surface matrix compared to the other. The coordinates at which the CCF achieves a maximum can be used as estimates of the "true" translation values at which a particular cell aligns best to its associated region. The `ccfMapPlot` function plots the CCF where function values are mapped to color. Additionally, the function will plot the cell/region pair for which the CCF map was determined. An orange square will be plotted on the region that visually indicates where the CCF "believes" the correct translation of the cell to be relative to the region. The plot below shows a particular cell/region pair and its associated CCF map from the known match comparison of Fadul 1-1 vs. Fadul 1-2. Note that the CCF max value is actually rather small in this instance. This is an artifact of how the CCF method is calculated using a Fast Fourier Transform technique. Effectively, any `NA` values in the scan, of which there are many, must be replaced prior to calculation of the CCF using FFTs. This often causes the CCF to be "deflated" relative the "true" CCF values. -->

<!-- ```{r} -->
<!-- kmCellRegionPairs$`-24`[27] %>% -->
<!--   map(~ cmcR::ccfMapPlot(mat1 = .[[1]], -->
<!--                          mat2 = .[[2]], -->
<!--                          theta = -24)) -->
<!-- ``` -->

<!-- In contrast, the plot below shows a particular cell/region pair and its associated CCF map from the known non-match comparison of Fadul 1-1 vs. Fadul 2-1. -->

<!-- ```{r} -->
<!-- knmCellRegionPairs$`-9`[30] %>% -->
<!--   map(~ cmcR::ccfMapPlot(mat1 = .[[1]], -->
<!--                          mat2 = .[[2]], -->
<!--                          theta = -9)) -->
<!-- ``` -->


<!-- ### $CCF_\max$ distribution  -->

<!-- Figure 4 of Tong et al. (2014) and Figure 5(a) of Chen et al. (2017) -->

<!-- ```{r} -->
<!-- ggplot() + -->
<!--   geom_histogram(data = kmComparisons %>% -->
<!--                    map2_dfr(.x = ., -->
<!--                             .y = names(.), -->
<!--                             ~ cmcR::topResultsPerCell(.x$comparison_1to2$ccfResults) %>% -->
<!--                               ungroup() %>% -->
<!--                               mutate(pair = rep(.y,times = nrow(.)))), -->
<!--                  aes(x = ccf,y = ..density..), -->
<!--                  fill = "orange", -->
<!--                  alpha = .7, -->
<!--                  binwidth = .03) + -->
<!--   geom_histogram(data = knmComparisons %>% -->
<!--                    map2_dfr(.x = ., -->
<!--                             .y = names(.), -->
<!--                             ~ cmcR::topResultsPerCell(.x$comparison_1to2$ccfResults) %>% -->
<!--                               ungroup() %>% -->
<!--                               mutate(pair = rep(.y,times = nrow(.)))), -->
<!--                  aes(x = ccf,y = ..density..), -->
<!--                  fill = "royalblue", -->
<!--                  alpha = .7, -->
<!--                  binwidth = .03) + -->
<!--   geom_bar(data = data.frame(x = c(.5,.5), -->
<!--                              y = c(0,0), -->
<!--                              comparisonType = c("known non-match","known match")), -->
<!--            aes(x = x,y = y,fill = comparisonType),stat = "identity", -->
<!--            alpha = .7) + -->
<!--   scale_fill_manual(values = c("orange","royalblue")) + -->
<!--   theme_bw() + -->
<!--   xlim(c(0,1)) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- bind_rows(kmComparisons %>% -->
<!--             map2_dfr(.x = ., -->
<!--                      .y = names(.), -->
<!--                      ~ cmcR::topResultsPerCell(.x$comparison_1to2$ccfResults) %>% -->
<!--                        ungroup() %>% -->
<!--                        mutate(pair = rep(.y,times = nrow(.)), -->
<!--                               comparisonType = "known match")), -->
<!--           knmComparisons %>% -->
<!--             map2_dfr(.x = ., -->
<!--                      .y = names(.), -->
<!--                      ~ cmcR::topResultsPerCell(.x$comparison_1to2$ccfResults) %>% -->
<!--                        ungroup() %>% -->
<!--                        mutate(pair = rep(.y,times = nrow(.)), -->
<!--                               comparisonType = "known non-match"))) %>% -->
<!--   ggplot(aes(x = ccf,fill = comparisonType)) + -->
<!--   geom_density(alpha = .5) + -->
<!--   theme_bw() + -->
<!--   scale_fill_manual(values = c("orange","royalblue")) + -->
<!--   xlim(c(0,1)) -->
<!-- ``` -->


<!-- ### Identified CMCs -->

<!-- Figure 7 of Tong et al. (2015) -->

<!-- ```{r} -->
<!-- kmCMCs <- kmComparisons %>% -->
<!--   map(~ cmcR::cmcFilter_improved(cellCCF_bothDirections_output = ., -->
<!--                                  consensus_function = median, -->
<!--                                  ccf_thresh = .6, -->
<!--                                  dx_thresh = 10, -->
<!--                                  theta_thresh = 3)) -->

<!-- knmCMCs <- knmComparisons %>% -->
<!--   map(~ cmcR::cmcFilter_improved(cellCCF_bothDirections_output = ., -->
<!--                                  consensus_function = median, -->
<!--                                  ccf_thresh = .6, -->
<!--                                  dx_thresh = 10, -->
<!--                                  theta_thresh = 3)) -->

<!-- cmcR::cmcPlot(x3p = fadul1.1$x3p, -->
<!--               cmcDF = kmCMCs$`1.1_1.2`$highCMCs) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- cmcR::cmcPlot(x3p = fadul1.1$x3p, -->
<!--               cmcDF = knmCMCs$`1.1_2.1`$initialCMCs[[1]]$comparison_1to2) -->
<!-- ``` -->


<!-- ### CMC Distribution -->

<!-- Figure 7 of Tong et al. (2014), Figure 9 of Tong et al. (2015), and Figure 6 of Chen et al. (2017) -->

<!-- ```{r} -->
<!-- bind_rows(kmCMCs %>% -->
<!--             map2_dfr(.x = ., -->
<!--                      .y = names(.), -->
<!--                      ~ .$highCMCs %>% -->
<!--                        mutate(pair = rep(.y,times = nrow(.)), -->
<!--                               comparisonType = "known match")), -->
<!--           knmCMCs %>% -->
<!--             map2_dfr(.x = ., -->
<!--                      .y = names(.), -->
<!--                      function(cmcs = .x,name = .y){ -->
<!--                        if(!is.null(cmcs$highCMCs)){ -->
<!--                        return(cmcs$highCMCs %>% -->
<!--                        mutate(pair = rep(name,times = nrow(.)), -->
<!--                               comparisonType = "known non-match")) -->
<!--                        } -->
<!--                        else{ -->
<!--                          cmcs$initialCMCs[[1]][[which.min(c(nrow(cmcs$initialCMCs[[1]]$comparison_1to2),nrow(cmcs$initialCMCs[[1]]$comparison_2to1)))]] %>% -->
<!--                            mutate(pair = rep(name,times = nrow(.)), -->
<!--                               comparisonType = "known non-match") %>% -->
<!--                            return() -->
<!--                        } -->
<!--                        })) %>% -->
<!--   group_by(pair,comparisonType) %>% -->
<!--   tally() %>% -->
<!--   ggplot(aes(x = n,fill = comparisonType)) + -->
<!--   geom_histogram(binwidth = 1) + -->
<!--   theme_bw() + -->
<!--   scale_fill_manual(values = c("orange","royalblue")) -->
<!-- ``` -->


## References

- Song, J. (2013).  Proposed “NIST Ballistics Identification System (NBIS)” Based on 3D Topogra-phy Measurements on Correlation Cells.American Firearm and Tool Mark Examiners Journal,45(2):11.

- Tong, M.,  Song,  J.,  and Chu,  W. (2015).  An Improved Algorithm of Congruent Matching Cells(CMC) Method for Firearm Evidence Identifications.Journal of Research of the National Institute of Standards and Technology, 120:102.

- Fadul T., Hernandez G., Stoiloff S. and Gulati Sneh “An Empirical Study to Improve the Scientific Foundation of Forensic Firearm and Tool Mark Identification Utilizing 10 Consecutively Manufactured Slides,” 2011 NCJRS 237960